Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2016-01-24 latex/article.tex
minor edit

\newcommand{\ie}{\emph{i.e.} }
\newcommand{\eg}{\emph{e.g.} }
\newcommand{\wrt}{\emph{w.r.t.} }
\newcommand{\wnlog}{w.l.o.g. }
\newcommand{\Zr}{\ensuremath{\mathbb{Z}[\rho]}}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\E}{\ensuremath{\mathcal{E}}}

@@

As illustrated in Figure~\ref{fig_quadtree_partitionning}-\emph{middle}, we
%propose a viewpoint dependent criterion to decide if a cell needs to be refined:
propose a viewpoint dependent criterion to decide if a cell needs to be refined:
the closer we are to the camera, the finer the cells are.
%In addition to the
%distance criterion, we define an angular criterion to prevent refining cells
%outside the camera frustrum.
Such a criterion is also well suited to GPU since it can be evaluated
independently on every cell.
%Hence, we can efficiently determine if a cell must be subdivided or not.
Figure~\ref{fig_lod_octree} illustrates our level of
details (LoD for short) criterion.
% we use. More precisely,
In dimension 2, if $\alpha$ denotes the viewing angle, an object at a distance $d$ from the camera
%with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is projected into more
has a projected size on screen of $2\cdot d\cdot\tan(\alpha)$.
%than one pixel
(see Figure~\ref{fig_lod_octree}-\emph{left}).
%Hence, the
Our distance criterion is based on the ratio (\emph{visibility ratio} in the
following) between the cell diameter $l(c)$ (power of 2 depending on the depth),
and its projected size. %$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
%center and the camera.
For a given cell $c$, split and merge decision are based
on this visibility ratio:
%
\begin{itemize}
  \item $c$ is split if its children
cells have a visibility ratio greater than  constant $k$\,;
  \item $c$ and its sibling cells are merged if their parent cell $c'$ has a visibility ratio lower than $k$\;
  \item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=3.5cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=3cm]{viewlod2_small}~~~~~
    %\includegraphics[width=3cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and angular criterion \emph{(right)}.
  %Based on LoD criterion evaluation, the cell buffer is updated between each frame \emph{(right)}.
  }\label{fig_lod_octree}
\end{figure}
%
%In addition to the distance criterion, we add an angular term in order
%to prevent subdivision of cells far from the camera frustrum (see
%Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
%details but please note that stay, split and merge decisions of all cells are computed in
%parallel from all cell morton codes.
Using such a criterion, split and merge decisions are computed in
%of all cells are computed in
parallel from the morton codes of all cells.

@@

\paragraph{Dynamic Refinement.} In this last approach, we want to optimize
the interactivity and the execution flow or parallelism on GPU\@. The
integration is simply computed using a regular grid at different
resolution $l$ (Fig.~\ref{fig:approx}-$right$). The shader code
becomes trivial (simple triple loop) and a lot of texture fetches are
involved, but interactivity can be easily obtained. Indeed, we
consider the following multi-pass approach:
\begin{enumerate}
\item When the surface geometry has been computed, we set the current
  level $l$ at an high level $l\EqDef l_{\max}$ of the mipmap
  pyramid.
\item We compute the integrals (and the curvature tensor) at the
  mipmap level $l$ and  send the estimated quantities to the
  visualization stage.
\item If the user changes the camera position or the computation
  parameters, we return to step 1.
\item If the current framerate is above a given threshold, we decrease
  $l$ and return to step 2 if the final $l_0$ level has not been
  reached yet.
\end{enumerate}
A consequence of the multi-pass approach is that when there is no
interaction (camera settings, parameters), the GPU automatically
refines the estimation. Even if step 2 is quite expensive, in
$O\left(\left({\frac{R}{2^l}}\right)^3\right)$, the interactive control
in step 3 considerably improves the interactive exploration of the
tensor with fast preliminary approximations which are quickly refined.

>>>>

\newcommand{\ie}{\emph{i.e.}\xspace}
\newcommand{\eg}{\emph{e.g.}\xspace}
\newcommand{\wrt}{\emph{w.r.t.}\xspace}
\newcommand{\wnlog}{w.l.o.g.\xspace}
\newcommand{\Zr}{\ensuremath{\mathbb{Z}[\rho]}}
\newcommand{\C}{\ensuremath{\mathbb{C}}}
\newcommand{\E}{\ensuremath{\mathcal{E}}}

@@

As illustrated in Figure~\ref{fig_quadtree_partitionning}-\emph{middle}, we
%propose a viewpoint dependent criterion to decide if a cell needs to be refined:
propose a viewpoint dependent criterion to decide if a cell needs to be refined:
the closer we are to the camera, the finer the cells are.
%In addition to the
%distance criterion, we define an angular criterion to prevent refining cells
%outside the camera frustrum.
Such a criterion is also well suited to GPU since it can be evaluated
independently on every cell.
%Hence, we can efficiently determine if a cell must be subdivided or not.
Figure~\ref{fig_lod_octree} illustrates our level of
details (LoD for short) criterion.
% we use. More precisely,
In dimension 2, if $\alpha$ denotes the viewing angle, an object at a distance $d$ from the camera
%with diameter greater than $2\cdot d\cdot\tan(\alpha)$ is projected into more
has a projected size on screen of $2\cdot d\cdot\tan(\alpha)$.
%than one pixel
(see Figure~\ref{fig_lod_octree}-\emph{left}).
%Hence, the
Our distance criterion is based on the ratio (\emph{visibility ratio} in the
following) between the cell diameter $l(c)$ (power of 2 depending on the depth),
and its projected size. %$2\cdot d_c\cdot\tan(\alpha)$, $d_c$ being the distance between the cell
%center and the camera.
For a given cell $c$, split and merge decision are based
on this visibility ratio:
%
\begin{itemize}
  \item $c$ is split if its children
cells have a visibility ratio greater than  constant $k$\,;
  \item $c$ and its sibling cells are merged if their parent cell $c'$ has a visibility ratio lower than $k$\,;
  \item otherwise, the cell $c$ stays for the next frame.
\end{itemize}
%
\begin{figure}[!h]
  \begin{center}
    \begin{overpic}[width=3.5cm]{figs/criterion}
      \put(33,40){$\alpha$}
      \put(50,45){$d_c$}
      \put(95,65){$l(c)$}
    \end{overpic}~~~~~
    \includegraphics[width=3cm]{viewlod2_small}~~~~~
    %\includegraphics[width=3cm]{subdivision}
  \end{center}
  \caption{Notations \emph{(left)} and adaptive meshing in dimension 2 using the LoD distance and angular criterion \emph{(right)}.
  %Based on LoD criterion evaluation, the cell buffer is updated between each frame \emph{(right)}.
  }\label{fig_lod_octree}
\end{figure}
%
%In addition to the distance criterion, we add an angular term in order
%to prevent subdivision of cells far from the camera frustrum (see
%Figure~\ref{fig_lod_octree}-\emph{middle}). We do not go into the
%details but please note that stay, split and merge decisions of all cells are computed in
%parallel from all cell morton codes.
Using such a criterion, split and merge decisions are computed in
%of all cells are computed in
parallel from the morton codes of all cells.

@@

\paragraph{Dynamic Refinement.} In this last approach, we want to optimize
the interactivity and the execution flow or parallelism on GPU\@. The
integration is simply computed using a regular grid at different
resolution $l$ (Fig.~\ref{fig:approx}-$right$). The shader code
becomes trivial (simple triple loop) and a lot of texture fetches are
involved, but interactivity can be easily obtained. Indeed, we
consider the following multi-pass approach:
\begin{enumerate}
\item When the surface geometry has been computed, we set the current
  level $l$ at an high level $l\EqDef l_{\max}$ of the mipmap
  pyramid.
\item We compute the integrals (and the curvature tensor) at the
  mipmap level $l$ and  send the estimated quantities to the
  visualization stage.
\item If the user changes the camera position or the computation
  parameters, we return to step 1.
\item If the current framerate is above a given threshold, we decrease
  $l$ and return to step 2 if the final $l_0$ level has not been
  reached yet.
\end{enumerate}
A consequence of the multi-pass approach is that when there is no
interaction (camera settings, parameters), the GPU automatically
refines the estimation. Even if step 2 is quite expensive, in
$O\left({\left({\frac{R}{2^l}}\right)}^3\right)$, the interactive control
in step 3 considerably improves the interactive exploration of the
tensor with fast preliminary approximations which are quickly refined.
